Untitled

### 2024-10-01 code/manuscript_altanalysis.Rmd
alt spec

---
title: "data_cleaning_longer_period"
author: "Justin"
date: "2023-08-15"
output: html_document
---

@@

# Libraries
```{r}
library(tigris)
library(tidygeocoder)

library(tidyverse)
library(readxl)
library(did)
library(Matching)
library(gtsummary)
library(RODBC)
library(ggpubr)
library(fixest)
library(kableExtra)
library(usmap)
library(did2s)
library(formattable)
library (readr)

library(did2s)
library(tidycensus)

`%notin%` <- Negate(`%in%`)
select <- dplyr::select

@@

## Formating plots

```{r, echo = FALSE, results = "asis", message=FALSE, warning = FALSE, fig.align="center"}

is.extrafont.installed <- function(){
  if(is.element("extrafont", installed.packages()[,1])){
    library(extrafont)
    # probably need something here to run font_import()
    return(T)
  }else{
    warning("Library extrafont installed; using system sans/serif libraries as fallback fonts. 
    To enable full font support, run: 
      install.packages('extrafont') 
      font_import()")
    return(F)
  }
}

# set font
base_font_family_tufte <- function(){
  if(is.extrafont.installed()){
    library(extrafont)
    tuftefont <- choose_font(c("Gill Sans MT", "Gill Sans", "GillSans", "Verdana", "serif"), quiet = FALSE)   #
  }else{
    tuftefont <- "serif"
  }
  return(tuftefont)
}

theme_tufte_revised <- function(base_size = 11, base_family = base_font_family_tufte(), ticks = TRUE) {

  ret <- theme_bw(base_family = base_family, base_size = base_size) + 
    theme(
      axis.line = element_line(color = 'black'),
      axis.title.x = element_text(vjust = -0.3), 
      axis.title.y = element_text(vjust = 0.8),
      legend.background = element_blank(), 
      legend.key = element_blank(), 
      legend.title = element_text(face="plain"),
      panel.background = element_blank(), 
      panel.border = element_blank(),
      panel.grid = element_blank(),
      plot.background = element_blank(),
      strip.background = element_blank()
    )

  if (!ticks) {
    ret <- ret + theme(axis.ticks = element_blank())
  }

  ret
}

# Data Prep

## Set study period
```{r}

included.years <- 2010:2023
included.treat <- 2013:2023

## Sites and ZipCodes
```{r}

## Zips
locs <- paste("/Users/markow/Dropbox/Git/UDS/UDS-", c(2012:2023), "-Full-Dataset.xlsx", sep = "")
uds.zip <- read_excel(locs[1], sheet = "HealthCenterZipCodes")[,c(1:4, 6, 5)]

#new.zip.names <- c("BHCMIS ID", "Grant Number", "Reporting Year" , "Zip Code", "Zip Code Type",  "None_Uninsured Patients" ,  "Medicaid_CHIP_Other Public Patients", "Medicare Patients", "Private Patients", "Total Number of Patients" )

uds.zip <- cbind(uds.zip, "Uninsured" = NA ,  "Medicaid" = NA, "Medicare" = NA, "Private" = NA)

new.zip.names <- colnames(uds.zip)

for(i in 2:length(locs)){
  temp.zip <- read_excel(locs[i], sheet = "HealthCenterZipCodes") #[,c(1:5, 10)]

  colnames(temp.zip) <- new.zip.names[c(1:5, 7:10, 6)]
  uds.zip <- rbind(uds.zip, temp.zip %>% mutate(ZipCode = str_pad(ZipCode, 5, pad = "0")))
}

uds.zip$ReportingYear <- as.numeric(uds.zip$ReportingYear)
uds.zip$NumberofPatients <- as.numeric(uds.zip$NumberofPatients)
uds.zip$Uninsured <- as.numeric(uds.zip$Uninsured)
uds.zip$Medicaid <- as.numeric(uds.zip$Medicaid)
uds.zip$Medicare <- as.numeric(uds.zip$Medicare)
uds.zip$Private <- as.numeric(uds.zip$Private)

uds.zip[is.na(uds.zip$NumberofPatients),]$NumberofPatients <- 0
uds.zip[is.na(uds.zip$Uninsured) & uds.zip$ReportingYear > 2012,]$Uninsured <- 0
uds.zip[is.na(uds.zip$Medicaid) & uds.zip$ReportingYear > 2012,]$Medicaid <- 0
uds.zip[is.na(uds.zip$Medicare) & uds.zip$ReportingYear > 2012,]$Medicare <- 0
uds.zip[is.na(uds.zip$Private) & uds.zip$ReportingYear > 2012,]$Private <- 0

uds.zip <- uds.zip[uds.zip$ZipCodeType == "ZipCode",]

## Bunk old Zip code code

# 
# # ## Rename
# # new.zip.names <- c("BHCMIS ID", "Grant Number", "Reporting Year" , "Zip Code", "Zip Code Type",  "None_Uninsured Patients" ,  "Medicaid_CHIP_Other Public Patients", "Medicare Patients", "Private Patients", "Total Number of Patients" ) 
# # colnames(uds.zip) <-    new.zip.names
# # 
# # 
# # ## Clean
# # 
# # uds.zip[uds.zip$`Total Number of Patients`== '-' | uds.zip$`Total Number of Patients`== '--',]$`Total Number of Patients` <- NA
# # uds.zip$`Total Number of Patients` <- as.numeric(uds.zip$`Total Number of Patients`)
# # uds.zip <- uds.zip[!is.na(uds.zip$`Total Number of Patients`),] %>% 
# #     mutate(`Reporting Year` = as.numeric(`Reporting Year`))
# # 
# # uds.zip$`None_Uninsured Patients` <- as.numeric(uds.zip$`None_Uninsured Patients`)
# # uds.zip$`Medicaid_CHIP_Other Public Patients` <- as.numeric(uds.zip$`Medicaid_CHIP_Other Public Patients`)
# # uds.zip$`Medicare Patients` <- as.numeric(uds.zip$`Medicare Patients`)
# # uds.zip$`Private Patients` <- as.numeric(uds.zip$`Private Patients`)
# # 
# # 
# # uds.zip <- cbind(uds.zip, broken.total = rowSums(uds.zip[,c(6:9)], na.rm = TRUE), missings = rowSums(is.na(uds.zip[,c(6:9)]))) %>% 
# #   mutate(`Total Number of Patients` = as.numeric(`Total Number of Patients`)) %>% 
# #   mutate(`Total Number of Patients` = ifelse(is.na(`Total Number of Patients`), round(missings*16/4), `Total Number of Patients`)) %>% 
# #   mutate(`None_Uninsured Patients` = ifelse(is.na(`None_Uninsured Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `None_Uninsured Patients`), 
# #          `Medicaid_CHIP_Other Public Patients` = ifelse(is.na(`Medicaid_CHIP_Other Public Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Medicaid_CHIP_Other Public Patients`), 
# #          `Medicare Patients` = ifelse(is.na(`Medicare Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Medicare Patients`), 
# #          `Private Patients` = ifelse(is.na(`Private Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Private Patients`))
# 
# 
# uds.zip$`Reporting Year` <- as.numeric(uds.zip$`Reporting Year`)
# uds.zip$`Total Number of Patients` <- as.numeric(uds.zip$`Total Number of Patients`)
# uds.zip$`None_Uninsured Patients` <- as.numeric(uds.zip$`None_Uninsured Patients`)
# uds.zip$`Medicaid_CHIP_Other Public Patients` <- as.numeric(uds.zip$`Medicaid_CHIP_Other Public Patients`)
# uds.zip$`Medicare Patients` <- as.numeric(uds.zip$`Medicare Patients`)
# uds.zip$`Private Patients` <- as.numeric(uds.zip$`Private Patients`)
# 
# 
# uds.zip[is.na(uds.zip$`Total Number of Patients`),]$`Total Number of Patients` <- 0
# uds.zip[grep("-", uds.zip$`None_Uninsured Patients`),]$`None_Uninsured Patients` <- 0
# uds.zip[grep("-", uds.zip$`Medicaid_CHIP_Other Public Patients`),]$`Medicaid_CHIP_Other Public Patients` <- 0
# uds.zip[grep("-", uds.zip$`Medicare Patients`),]$`Medicare Patients` <- 0
# uds.zip[grep("-", uds.zip$`Private Patients`),]$`Private Patients` <- 0
# 
# uds.zip.totals <- uds.zip %>%
#   select(`Grant Number`, `Reporting Year`, `None_Uninsured Patients`:`Total Number of Patients`) %>%
#   group_by(`Grant Number`, `Reporting Year`) %>% summarise(None = sum(`None_Uninsured Patients`, na.rm = T),
#                                                            MCR = sum(`Medicare Patients`, na.rm = T),
#                                                            COM = sum(`Private Patients`, na.rm = T),
#                                                            MCD = sum(`Medicaid_CHIP_Other Public Patients`, na.rm = T),
#                                                            Total = sum(`Total Number of Patients`, na.rm = T))
# 
# uds.zip <- uds.zip[uds.zip$`Zip Code Type` == "ZipCode",]

## Sites
locs <- paste("/Users/markow/Dropbox/Git/UDS/UDS-", c(2012:2023), "-Full-Dataset.xlsx", sep = "")

uds.sites <- read_excel(locs[1], sheet = "HealthCenterSiteInfo") %>% 
  select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>% 
  mutate(Year = 2012)

colnames(uds.sites) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")

for(i in 2:3){
site.temp <- read_excel(locs[i], sheet = "HealthCenterSiteInfo") %>% 
                       select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, 
                              SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>%
  mutate(Year = 2011 + i)

colnames(site.temp) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")

   uds.sites <-  rbind(uds.sites, site.temp)
}

for(i in 4:(length(locs)-3)){
  uds.sites <- rbind(uds.sites, read_excel(locs[i], sheet = "HealthCenterSiteInfo") %>% 
                       select("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code") %>% 
  mutate(Year = 2011 + i))
}

## 2021
temp.sites <- read_excel(locs[i+1], sheet = "HealthCenterSiteInfo" )%>% 
  select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>% 
  mutate(Year = 2021)
colnames(temp.sites) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")

uds.sites <- rbind(uds.sites, temp.sites)

## 2022
temp.sites <- read_excel(locs[i+2], sheet = "HealthCenterSiteInfo" )%>% 
  select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>% 
  mutate(Year = 2022)
colnames(temp.sites) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")

uds.sites <- rbind(uds.sites, temp.sites)

## 2023
temp.sites <- read_excel(locs[i+3], sheet = "HealthCenterSiteInfo" )%>% 
  select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>% 
  mutate(Year = 2023)
colnames(temp.sites) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")

uds.sites <- rbind(uds.sites, temp.sites)

uds.sites.old <- read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Sites.csv", colClasses = "character") %>% 
  mutate(Year = as.numeric(Year))

colnames(uds.sites.old) <- c("BHCMIS ID", "Health Center Name", "Site Name", "Site Street Address", "Site Street Address 2", "Site State", "Site ZIP Code", "Year", "GranteeID", "Site Street Address 3","Site City","ModernGrateeID")

uds.sites.full <- bind_rows(uds.sites, uds.sites.old) %>% 
  arrange(`BHCMIS ID`, Year) %>% 
  select(`BHCMIS ID`:`Health Center Name`, Year, `Site Name`, `Site Street Address`, `Site Street Address 2`, `Site Street Address 3`, `Site City`, `Site State`, `Site ZIP Code` , `Site Type`:`Total Weekly Hours Of Operation`)

uds.sites.full$Zip <- substr(uds.sites.full$`Site ZIP Code`, 1, 5)

uds.sites.full <- uds.sites.full %>% 
  filter(`Site State` %notin% c('GU','VI','PW','MH','AS','FM','PR','MP')) #'AK','HI',

uds.sites.full[grep(pattern = "-", uds.sites.full$Zip),]$Zip <- NA

#write.csv(x = uds.sites.full, file = "//Users/markow/Dropbox/Git/APMs/data_processed/Sites96to21.csv")

uds.sites %>% 
  filter(Year %in% c(2021, 2022, 2023)) %>% 
  arrange(`Grant Number`, Year)

## Clean up the missing addresses, geocoding

tbcoded <- uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]
coded <- geo(street = tbcoded[c(1:1000),]$`Site Street Address`, 
             city = tbcoded[c(1:1000),]$`Site City`, 
             state = tbcoded[c(1:1000),]$`Site State`, 
             method = "census", 
             full_results = TRUE)

for (g in 1:16){
  g
coded <- rbind(coded, 
               geo(street = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site Street Address`, 
             city = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site City`, 
             state = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site State`, 
             method = "census", 
             full_results = TRUE) )
}

coded <- rbind(coded, 
               geo(street = tbcoded[c(17001:17152),]$`Site Street Address`, 
             city = tbcoded[c(17001:17152),]$`Site City`, 
             state = tbcoded[c(17001:17152),]$`Site State`, 
             method = "census", 
             full_results = TRUE) )

coded[grep(pattern = "[[:digit:]]{5}$", coded$matched_address),]

uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]$Zip <- str_extract(coded$matched_address, pattern = "[[:digit:]]{5}$")
uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]

uds.sites.full.temp <- uds.sites.full

uds.sites.full <- uds.sites.full.temp

uds.sites.full.temp %>% filter(`Grant Number` %in% c("H80CS00881") & Year == 2016)

chc <- read.csv("//Users/markow/Dropbox/Git/Competition/data_raw/chc.csv")

chc %>% filter(Health.Center.Number %in% c("H80CS00881"))

uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] <- uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] %>%
  left_join(chc, by = c("Grant Number" = "Health.Center.Number", "Site Street Address" = "Site.Address")) %>%
  mutate(Zip = ifelse(is.na(Zip), substr(Health.Center.Organization.ZIP.Code, 1, 5), Zip)) %>%
  select(`BHCMIS ID`:Zip) %>%
  unique()

uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] <- uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] %>%
  left_join(chc, by = c("Grant Number" = "Health.Center.Number", "Site Name" = "Site.Name")) %>%
  mutate(Zip = ifelse(is.na(Zip), substr(Health.Center.Organization.ZIP.Code, 1, 5), Zip)) %>%
  select(`BHCMIS ID`:Zip) %>%
  unique()

uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]
```

table(uds.sites.full.temp$`Location Setting`)

uds.sites.full <- uds.sites.full %>% #filter(`Location Type` == "Permanent" & `Location Setting` %in% c("All Other Clinic Types")) %>% 
  mutate(Access = as.numeric(ifelse(`Total Weekly Hours Of Operation` == "-" & `Operational Schedule` == "Full-Time", 40, 
                  ifelse(`Total Weekly Hours Of Operation` == "-" & `Operational Schedule` == "Part-Time", 10, `Total Weekly Hours Of Operation`))))

uds.sites.full[is.na(uds.sites.full$Zip),]

uds.sites.full %>% 
  arrange(`Total Weekly Hours Of Operation`, `Operational Schedule` )

## Read in census data for all zip codes
```{r}

census <- data.frame(ZipCode = 0, NAME = 0, YEAR = 0, 
                     TotalPop = 0,
                     Male = 0, Female = 0, 
                     AgeUnder18 = 0, Age18to64 = 0, Age65andOver = 0, 
                     White = 0, Black = 0, AIAN = 0, Asian = 0, MR = 0, Hispanic = 0, EducLow = 0, EducMid = 0, EducHigh = 0, 
                     PovertyStatusDet = 0, IncomeBelowPoverty = 0, Unemployed = 0, Unemp_denom = 0, 
                     MCD.denom = 0, Medicaid = 0, Unins.denom = 0, Uninsured = 0)

for (i in 1:11){
  census <- rbind(census, get_acs(geography = "zcta", survey = "acs5",
                       variables = c("B01003_001","B17001_001","B17001_002","B01001_002","B01001_026",
                                     "B02001_002","B02001_003","B02001_004","B02001_005","B02001_006","B02001_008",
                                     "B03001_003", 
                                     "B01001_003","B01001_004","B01001_005","B01001_006","B01001_007","B01001_008","B01001_009",
                                     "B01001_010","B01001_011","B01001_013","B01001_014","B01001_015","B01001_016","B01001_017",
                                     "B01001_018","B01001_019","B01001_020","B01001_021","B01001_022","B01001_023","B01001_024","B01001_025",
                                     "B01001_027","B01001_028","B01001_029","B01001_030","B01001_031","B01001_032","B01001_033","B01001_034",
                                     "B01001_035","B01001_036","B01001_037","B01001_038","B01001_039","B01001_040","B01001_041","B01001_042","B01001_043",
                                     "B01001_044","B01001_045","B01001_046","B01001_047","B01001_048","B01001_049",
                                     "B06009_002","B06009_003", "B06009_004","B06009_005","B06009_006",
                                     "B23025_002","B23025_005",
                                     "C27007_001", "C27007_004", "C27007_007", "C27007_010", "C27007_014", "C27007_017", "C27007_020",
                                     "B18135_001","B18135_007","B18135_012","B18135_018","B18135_023","B18135_029","B18135_034"), 
                       year = 2011 + i) %>% 
  pivot_wider(id_cols = c(GEOID, NAME), names_from = variable, values_from = estimate) %>% 
    mutate(YEAR = 2011 + i, TotalPop = B01003_001, PovertyStatusDet = B17001_001, IncomeBelowPoverty = B17001_002,
           AgeUnder18 = B01001_003 + B01001_004 + B01001_005 + B01001_006 + B01001_027 + B01001_028 + B01001_029 + B01001_030,
           Age18to64 = B01001_007 + B01001_008 + B01001_009 + B01001_010 + B01001_011 + B01001_013 + B01001_014 + B01001_015 + 
                       B01001_016 + B01001_017 + B01001_018 + B01001_019 + B01001_031 + B01001_032 + B01001_033 + B01001_034 +
                       B01001_035 + B01001_036 + B01001_037 + B01001_038 + B01001_039 + B01001_040 + B01001_041 + B01001_042 + B01001_043, 
           Age65andOver = B01001_020 + B01001_021 + B01001_022 + B01001_023 + B01001_024 + B01001_025 + 
                          B01001_044 + B01001_045 + B01001_046 + B01001_047 + B01001_048 + B01001_049, 
           Male = B01001_002, Female = B01001_026, 
           White = B02001_002, Black = B02001_003, AIAN = B02001_004, Asian = B02001_005 + B02001_006, MR = B02001_008, 
           Hispanic = B03001_003, 
           EducLow = B06009_002, EducMid = B06009_003 + B06009_004, EducHigh = B06009_005 + B06009_006,
           Unemployed = B23025_005, Unemp_denom = B23025_002,
           MCD.denom = C27007_001	, Medicaid = C27007_004	 + C27007_007 + C27007_010	+ C27007_014 + C27007_017 + C27007_020,
           Unins.denom = B18135_001, Uninsured = B18135_007 + B18135_012 + B18135_018 + B18135_023 + B18135_029 + B18135_034) %>% 
    select(ZipCode = GEOID, NAME, YEAR, TotalPop:Uninsured))

  print(i)
}
census <- census[-1,]

##########
census$ZipCode <- substr(census$NAME, 7, 11)
#census$ZipCode <- str_pad(census$ZipCode, 5, pad = "0")

census %>% 
  filter(YEAR == 2022) %>% 
  select(ZipCode) %>% 
  #unique() %>% 
  table() %>% 
  table()
```

## Merge with Older UDSs 1996-2011
```{r}
uds.cw <- read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_CW.csv", colClasses = "character") %>% 
  mutate(link.ID = ifelse(is.na(ModernGranteeID) & !is.na(LongGrantID) & Year != 2010, LongGrantID, 
                   ifelse(is.na(ModernGranteeID) & !is.na(GranteeID), GranteeID, BHCMIS.ID)), 
         Year = as.integer(Year))

uds.cw %>% 
  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(BHCMIS.ID == '010060' & Year %in% c(2007:2011)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L5A_CA, T3B_L6_CA, T3B_L1_CA, T3B_L8_CA, T3B_L4_CA, T3B_L12_CA)

namevec <- c("BHCMIS.ID", "Year", "NHA", "NHB", "HL", "NHW", "Total", "Eng2ndLang")

#fins.revenue.expenses <- read_csv("FQHC_Revenue_vs_Expenses.csv")
#cw <- read_excel("UDS-990 Crosswalk.xlsx")

## Total Patients served by Year
```{r}
read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv") %>% 
  select(Year, T3B_L4_CA) %>% 
  group_by(Year) %>% 
  summarise(sum(T3B_L4_CA, na.rm = TRUE))

## Clinic-level in Covariates 
```{r}

# Table 3B

uds.3B.2012 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2013 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)

uds.3B.2014 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2015 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table3B", skip = 2) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2016 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

uds.3B.2017 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2018 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2019 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

uds.3B.2020 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2021 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2022 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2022-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2023 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2023-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

namevec <- c("Year", "BHCMISID", "ModernGranteeID", "NHA", "NHB", "HL", "NHW", "Total", "Eng2ndLang")
uds.3B <- rbind(cbind(Year = 2012, uds.3B.2012),
                cbind(Year = 2013, uds.3B.2013),
                cbind(Year = 2014, uds.3B.2014),
                  cbind(Year = 2015, uds.3B.2015),
                  cbind(Year = 2016, uds.3B.2016),
                  cbind(Year = 2017, uds.3B.2017),

                  cbind(Year = 2018, uds.3B.2018),
                  cbind(Year = 2019, uds.3B.2019), 
                  cbind(Year = 2020, uds.3B.2020),
                  cbind(Year = 2021, uds.3B.2021),

                  cbind(Year = 2022, uds.3B.2022),
                  cbind(Year = 2023, uds.3B.2023)) %>%

  rename_all(vars(namevec), function(x) namevec)

uds.3B <- rbind(
  uds.cw %>% 
  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2007)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L5A_CA, T3B_L6_CA, T3B_L1_CA, T3B_L8_CA, T3B_L4_CA, T3B_L12_CA) %>% 
    setNames(namevec), 
  uds.cw %>% 
  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2008)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L5A_CA, T3B_L6_CA, T3B_L1_CA, T3B_L8_CA, T3B_L4_CA, T3B_L12_CA) %>% 
    setNames(namevec),
    uds.cw %>% 
  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2009)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L1_CB, T3B_L3_CB, T3B_L8_CA, T3B_L5_CB, T3B_L8_CD, T3B_L12_CA) %>% 
    setNames(namevec), 
  uds.cw %>% 
  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2010)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L1_CB, T3B_L3_CB, T3B_L8_CA, T3B_L5_CB, T3B_L8_CD, T3B_L12_CA) %>% 
    setNames(namevec), 
  uds.cw %>% 
  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2011)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L1_CB, T3B_L3_CB, T3B_L8_CA, T3B_L5_CB, T3B_L8_CD, T3B_L12_CA) %>% 
    setNames(namevec), 
  uds.3B)
uds.3B %>% 
  arrange(BHCMISID, Year)

>>>>

---
title: "Untitled"
author: "Justin"
date: "2024-10-01"
output: html_document
---

@@

```{r}
library(readxl)
library(did2s)
library(tidyverse)
library(directlabels)
library(gtsummary)
library(kableExtra)
library(ggpubr)
library(tigris)
library(usmap)
```

```{r}
mean.nas<- function(x){ mean(x, na.rm = TRUE)}

options(scipen=999)
```

```{r}
dfc <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
uds.sites.full <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/sites_geocoded.csv") %>%
  mutate(Access = ifelse(`BHCMIS ID` == "080170" & as.numeric(`Total Weekly Hours Of Operation`) > 40000, 4, Access))
clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
  #filter(Year >= included.years[1]) %>%
  group_by(Zip, Year) %>%
  summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>%
  arrange(desc(Clinics))

 uds.sites.full %>%
   filter(is.na(Zip))

@@

# Build Variables

## Z
